---
title: "Hopkins Machine Learning Project Report"
author: "Andy Hasselwander"
date: "February 16, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(caret, echo=FALSE)

if(!exists("training")){
training <- read.csv(url("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"))}

if(!exists("testing")){
testing <- read.csv(url("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"))}

```
Source: Velloso, E.; Bulling, A.; Gellersen, H.; Ugulino, W.; Fuks, H. Qualitative Activity Recognition of Weight Lifting Exercises. Proceedings of 4th International Conference in Cooperation with SIGCHI (Augmented Human '13) . Stuttgart, Germany: ACM SIGCHI, 2013.

Read more: http://groupware.les.inf.puc-rio.br/har#wle_paper_section#ixzz57ISl7FAA

One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).

The goal of your project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set. You may use any of the other variables to predict with. You should create a report describing how you built your model, how you used cross validation, what you think the expected out of sample error is, and why you made the choices you did. You will also use your prediction model to predict 20 different test cases.

A: Exactly according to specifications
B: Throwing the elbows to the front
C: Lifting the dumbbell only halfway
D: Lowering the dumbbell only halfway
E: Throwing the hips to the front

#Exploratory Analysis
```{r}
library(ISLR); library(ggplot2); library(caret);
summary(training)

#Create a vector of anything not a predictive variable
ignoreVector <- c(1:7,160)

sum(complete.cases(training[,-ignoreVector]))
#Too few cases to use only complete cases

sumCC <- function(x) {sum(complete.cases(x))}

ccVector <- apply(training[-ignoreVector], 2,  sumCC)

```




#Variable Reduction
```{r}


preProc <- preProcess(training[,-ignoreVector], method="pca")
prComp <- princomp(training[,-ignoreVector])



```